Preregistration analysis, Cost 2 study

### 2019-06-02 Cost2/Cost2_prereg.Rmd
typo

``` {r 16.3.3. OC modeling, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# group
summaryOC <- list()
summaryOC$all <- dataAll %>%
                 filter(Choice < 2) %>%
                 group_by(Cost, SubjID) %>%
                 do(optimizeOCModel(., simplify = T)) %>%
                 ungroup()

>>>>

``` {r 16.3.3. OC modeling, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# group
summaryOC <- list()
summaryOC$all <- dataAll %>%
                 filter(Choice < 2) %>%
                 rename(Offer = Reward) %>%
                 group_by(Cost, SubjID) %>%
                 do(optimizeOCModel(., simplify = T)) %>%
                 ungroup()
